Presentasjon OPX Fiffig tittel

### 2022-08-02 Presentasjon/presentasjon.Rmd
Sletter og renamer bildefiler, adder css fil

---
title: "Presentasjon OPX Fiffig tittel"
author: "Gruppe 5"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

@@

## {data-background="Images/start1.png" data-background-size=cover}

## <br> OPX and their goal
- A startup developing solutions for socially responsible investment strategies
- The goal is to increase cash flow to charitable purposes 
- Donors' trust in NGOs' financial performance and their ability to deliver results is crucial for their choice of beneficiaries <br>

@@

@@

>>>>

---
title: "Presentasjon OPX Fiffig tittel"
author: "Gruppe 5"
date: "4.8.2022"
output: 
  ioslides_presentation: 
    css: stylesss.css
---

@@

## <br> OPX and their goal
- Develop solutions for socially responsible investment strategies
- Increase cash flow to charitable purposes <br>

@@

----
```{r, out.height="360", out.width="612", fig.align='center'}
knitr::include_graphics("Images/fcuk.png")

@@

## <iframe width="1280" height="720" src="Images/henrik.mp4" align="middle" frameborder="0" allowfullscreen></iframe>

## {data-background="Images/tenke.png" data-background-size=cover}

## <br> Our experience

- Unsolvable case due to non-existent data
- Hard to create credible KPIs due to limited knowledge of economics and the NGO sector
- **Insight into real-life work challenges - the clash between is desired and what is possible**
